\chapter{Conclusion}

This chapter presents the overall conclusion of the first phase of Project Koschei. It summarizes the current state of system development, the milestones achieved, and the goals set for the upcoming semester. The chapter highlights the successful establishment of the architectural foundation and outlines the future direction toward full system integration and AI behavior refinement.

\section{Plan for Next Semester}

The primary objective for the next semester is to advance the prototype into a fully functional system integrating all core modules. The focus will shift from establishing the framework to refining AI behavior, developing story-driven gameplay, optimizing multiplayer performance, and enhancing user experience.

\begin{itemize}
    \item \textbf{Full Integration of AI Systems:}  
    Connect the Ollama-based LLM seamlessly with Unity's in-game chat system through FastAPI, enabling real-time contextual dialogue and style-based imitation~\cite{park2023generative,kolenbrander2023}.
    
    \item \textbf{Enhanced Memory and Context Handling:}  
    Expand the ChromaDB collections to include event tracking, suspicion updates, and persistent contextual memory for each AI entity~\cite{liu2022,wangw2024,hong2025}.
    
    \item \textbf{Advanced AI Behavior and Decision Logic:}  
    Implement the Alien-01's strategic reasoning, deception, and adaptive responses using the behavior tree and reinforcement-learning modules~\cite{hagendorff2023,park2023ai,poje2023}.
    
    \item \textbf{Story and Narrative Integration:}  
    Design and implement a cohesive narrative layer that ties player objectives, AI motivations, and environmental storytelling into a consistent experience. The narrative will evolve dynamically based on player interactions and AI deception outcomes, enhancing immersion and replayability. Environmental cues, mission logs, and AI-generated dialogue will reflect the unfolding story and player choices.
    
    \item \textbf{Networking Optimization:}  
    Strengthen multiplayer synchronization using Unity Netcode, ensuring smooth gameplay across connected clients with minimal latency~\cite{barri2016,deng2018,motoo2021}.
    
    \item \textbf{UI and UX Improvements:}  
    Improve the chat system with visual message grouping, timestamps, and player proximity effects. Introduce player indicators and role-specific interface elements~\cite{raith2021}.
    
    \item \textbf{Testing and Evaluation:}  
    Conduct controlled multiplayer tests to evaluate AI believability, narrative consistency, latency performance, and dialogue coherence under varied game scenarios~\cite{yoo2023,danry2023}.
\end{itemize}

By the end of the next semester, Project Koschei is expected to evolve into a stable, interactive multiplayer experience featuring dynamic AI-driven dialogue, narrative adaptation, and decision-making~\cite{zeng2023,mikros2023}.

\section{Summary}

This chapter concludes the design and development progress of the current semester. The foundational systems—Unity game environment, networking framework, AI backend, and database integration—have been successfully implemented~\cite{barri2016,chen2023}. The groundwork for AI-driven communication, memory management, and initial world-building has been established through FastAPI and ChromaDB integration~\cite{muludi2023,chandrasekhara2024}.

The upcoming development phase will focus on expanding the system's intelligence, refining the dynamic story framework, and improving real-time responsiveness. Integrating narrative progression with AI deception and adaptive dialogue will form the emotional and experiential core of the final product. With its modular and scalable architecture, Project Koschei is well-positioned to deliver an innovative fusion of multiplayer interaction, emergent storytelling, and adaptive artificial intelligence in the following semester.
ptimizing multiplayer performance, and enhancing user experience.

