\chapter{Introduction}

\section{Background}

Large Language Models have revolutionized natural language processing, yet face challenges in dynamic, real-time social environments. Traditional game AI relies on fixed logic trees and scripted behaviors, creating a "believability gap" between player expectations and predictable AI patterns.

Recent research shows memory-augmented LLMs can maintain contextual awareness across extended interactions~\cite{liu2022,wangw2024}. Studies on generative agents~\cite{park2023generative} and stylometric analysis~\cite{mikros2023} demonstrate LLMs can mimic communication patterns and maintain consistent personas. This project leverages these breakthroughs to create an AI-controlled impostor engaging in sophisticated social deception within a 3D multiplayer environment.

Set in a fictionalized Chernobyl Exclusion Zone, players investigate unexplained disappearances linked to Soviet research. Unlike traditional voting-based social deduction games, this introduces combat-based verification and continuous proximity communication. The alien impostor uses a locally hosted LLM with vector memory, emotion-aware dialogue, and stylometric mimicry~\cite{kolenbrander2023}.

\section{Problem Definition}

Current LLM implementations face three critical limitations in multiplayer gaming:

\textbf{Memory and Consistency:} LLMs forget established facts and fail to maintain coherence across sessions~\cite{wangy2024}, creating immersion-breaking contradictions.

\textbf{Emotional Adaptability:} Existing agents lack dynamic tone adjustment based on suspicion levels, proximity threats, or conversational dynamics, resulting in robotic responses.

\textbf{Style Replication:} LLMs struggle to mimic individual communication patterns—slang, punctuation, sentence structure, vocabulary~\cite{mikros2023}—making AI impostors easily identifiable.

These limitations prevent LLMs from functioning as believable social agents where deception, trust-building, and adaptive communication are essential~\cite{yoo2023,hagendorff2023}.

\section{Scope and Motivation}

The project develops a 3D first-person multiplayer social deduction game with:

\begin{itemize}
\item Chernobyl-inspired environment with mission objectives, NPC interactions, and combat mechanics supporting four synchronized players~\cite{barri2016,deng2018}.

\item Locally hosted memory-augmented LLM capable of real-time deception, player impersonation, and adaptive dialogue through proximity chat~\cite{hong2025}. AI employs retrieval-augmented generation using ChromaDB/FAISS for conversational history~\cite{chen2023,muludi2023}.

\item AI systems including trust graph modeling, stylometric mimicry, shapeshifting, and Theory of Mind tracking player knowledge~\cite{park2023ai,poje2023}.
\end{itemize}

Focus areas: LLM interaction architecture, game logic integration, AI deception. Excludes procedural generation—environment is manually designed. 

Motivation: bridge the believability gap, advance LLM-powered autonomous agents, and investigate natural LLM behavior in group social scenarios~\cite{zeng2023}.

\section{Objectives}

Seven primary objectives:

\textbf{1. Believable Social Deception:} Generate plausible lies, deflect suspicion, manipulate trust using memory-augmented awareness~\cite{yoo2023,danry2023}. Target: AI survives unidentified in 30\% of sessions.

\textbf{2. Dynamic Linguistic Adaptation:} Real-time chat analysis extracting patterns and sentiment. Generate dialogue mimicking vocabulary, sentence structure, punctuation, and tone~\cite{mikros2023,kolenbrander2023}.

\textbf{3. Memory-Augmented Architecture:} Implement ChromaDB/FAISS for recalling events, conversations, facts~\cite{liu2022,chandrasekhara2024}. Three collections: player messages, game events, NPC memory~\cite{wangw2024}.

\textbf{4. Combat-Based Verification:} Novel mechanic resolving suspicion through direct confrontation, not voting—pioneering active verification with skill-based gameplay.

\textbf{5. Real-Time Performance:} AI response latency under 2 seconds~\cite{motoo2021}. Optimize local LLM inference, memory retrieval, Unity-backend communication.

\textbf{6. Robust Multiplayer Framework:} Stable, low-latency environment using Unity Netcode/Photon Fusion~\cite{barri2016,deng2018}. Synchronize actions, interactions, proximity chat with 99.9\% uptime.

\textbf{7. Immersive Experience:} Detailed Chernobyl environment balancing psychological tension with tactical gameplay~\cite{raith2021}.

\section{Risks \& Challenges}

\subsection{AI Performance Risk}
LLM may generate nonsensical dialogue or respond slowly. Mitigation: local hosting, model quantization, RAG memory system~\cite{chen2023,muludi2023}, strict prompts.

\subsection{Integration Complexity}
Unity-Python interface bottlenecks. Mitigation: gRPC protocols, clear API contracts, asynchronous processing.

\subsection{AI Balance}
Too strong or weak AI. Mitigation: separate cognitive/combat abilities, extensive playtesting, dynamic difficulty adjustment.

\subsection{Toxicity Risk}
AI replicating toxic behavior~\cite{park2023ai}. Mitigation: ethical guidelines, automated filtering, hard constraints preventing harassment imitation.

\subsection{Memory Consistency}
Database retrieval failures or inconsistent alibis~\cite{wangw2024}. Mitigation: consistency checker, metadata filters, reliability scores.

\subsection{Synchronization Issues}
LLM delays causing desync~\cite{motoo2021}. Mitigation: async-tolerant architecture, message queuing, timestamp-based ordering.

\section{Assumptions}

\begin{itemize}
\item Players actively engage in text communication
\item LLM responds within 2 seconds (Llama 3.1:8b locally)
\item ChromaDB/FAISS retrieves context within 100-200ms~\cite{chen2023}
\item Players exhibit distinctive communication styles~\cite{mikros2023}
\item Consumer hardware: quad-core CPU, 8-16GB RAM minimum; 6-core, 16-32GB, RTX 2060+ recommended
\end{itemize}

\section{Societal / Industrial Relevance}

\hspace{.7cm}\textbf{Gaming Innovation:} Novel NPC AI beyond scripted behaviors toward adaptive, psychologically complex characters~\cite{park2023generative,zeng2023}.

\textbf{AI Research:} Controlled environment studying trust dynamics, deception modeling, Theory of Mind, long-term memory~\cite{park2023ai,poje2023,hagendorff2023}.

\textbf{Cybersecurity:} Realistic human communication imitation for social engineering simulation and training~\cite{danry2023}.

\textbf{Training Systems:} Memory-augmented dialogue and emotion-aware responses for crisis negotiation, communication training, scenario-based learning~\cite{kolenbrander2023}.

\textbf{Human-AI Studies:} Dataset generation on interaction patterns, trust formation, deception detection, social reasoning informing AI alignment and safety.

\section{Report Organization}
\hspace{.7cm}\textbf{Chapter 1:} Background, problem definition, scope, objectives, risks, assumptions, relevance.

\textbf{Chapter 2:} Literature survey on memory-augmented LLMs, social deception, stylometry, networking, autonomous agents—identifying research gaps.

\textbf{Chapter 3:} System architecture, design diagrams, components, algorithms, requirements, database, module division, timeline, UI design.

\textbf{Chapter 4:} Contributions summary and next semester implementation plan.

Appendices contain design presentation, institutional requirements, and CO-PO-PSO mapping.

\section{Summary}

Project Koschei is a multiplayer game leveraging memory-augmented LLMs for real-time social deception, addressing LLM limitations in dynamic social settings: memory consistency, emotional adaptability, and style mimicry~\cite{yoo2023,hagendorff2023,danry2023}.

The system integrates locally hosted LLM with vector memory~\cite{liu2022,wangw2024}, emotion-aware dialogue~\cite{kolenbrander2023}, and stylometric mimicry~\cite{mikros2023} in a 3D Chernobyl environment. Seven objectives guide development: social deception, linguistic adaptation, memory architecture, combat verification, real-time performance, multiplayer infrastructure, and immersive experience.

Identified risks include AI performance, integration complexity, balance, toxicity, memory consistency, and synchronization, with mitigation strategies. Key assumptions cover player engagement, LLM latency, database performance, distinctive styles, and hardware capabilities.

Beyond gaming, the project advances AI research, cybersecurity training, simulation learning, and human-AI interaction studies~\cite{park2023ai,raith2021}. Following chapters detail literature survey, system design, and implementation planning.

